r5r: Rapid Realistic Routing with R5 in R

### 2020-09-18 r-package/paper2020/paper2020.Rmd
updates visualization paper section

dasdasdds

@@

`detailed_itineraries()` output is a `sf` object, which means that each trip segment is associated to a geometry

```{r, message = FALSE}
# extract OSM network
street_net <- street_network_to_sf(r5r_core)

# plot
ggplot() +
   geom_sf(data = street_net$edges, color='gray85') +
   theme_minimal()

```

>>>>

@@

`detailed_itineraries()` output is a `sf` object, which means that each trip 
segment is associated to a spatial geometry that can be plotted with common `R` 
packages, such as `ggplot2`. The package also offers a handy 
`street_network_to_sf()` function that extracts the OSM street network used in 
the routing as a `sf` object and can be used to provide geographic context for 
the visualization.

```{r, message = FALSE, fig.width = 7, fig.height = 5}
# extract OSM network
street_net <- street_network_to_sf(r5r_core)

dit$facet_labels <- paste0(dit$fromId, " to\n", dit$toId)

ggplot() +
   geom_sf(data = street_net$edges, color = "gray85") +
   geom_sf(data = dit, aes(color = mode), size = 1) +
   facet_wrap(~ facet_labels, nrow = 1) +
   theme_minimal() + 
   theme(legend.position = "bottom", axis.text.x = element_text(angle = 30, hjust = 1))
```
